A comparison of design-based and model-based approaches for spatial data.

### 2021-09-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.Rmd
Added Jay's comments to the manuscript.

@@

@@

@@

Finite Population Block Kriging (FPBK) is a model-based approach that expands the geostatistical Kriging framework to the finite population setting [@verhoef2008spatial]. Instead of basing inference off of a specific sampling design, we assume the data are generated by a spatial process. @verhoef2008spatial gives details on the theory of FPBK, but some of the basic principles are summarized below. Let $\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}$ be a response variable that can be measured at the $N$ population units and is represented as an $N \times 1$ vector. Suppose we want to predict some linear function of the response variable, $f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}$, where $\mathbf{b}^\prime$ is a $1 \times N$ vector of weights. For example, if we want to predict the population total across all population units, then we would use a vector of 1's for the weights.

@@

@@

>>>>

__Jay VH__: I think it is important to stress that the limiting distribution is over all possible randomizations, constrained by whatever design is used.

__Jay VH__: quantity is vague. We should stick with variables, or realized variables (we might also call these values, but we should define and establish a consistent terminology early on.) __Matt H__: I think, though this comment is for this paragraph, we should establish the terminology earlier.

@@

__Jay VH__: What about the design for model-based inference? Strictly speaking, it is fixed – there is no probabilistic use of a randomized design. However, we are going to have to deal with Diggle et al. (2010).

@@

__Jay VH__: Saying "the distribution of the sampled population units mirrors the density of..." is confusing to me. Are these formal statistical definitions of distribution (cumulative distribution function) and density (probability density function)? Wouldn’t IRS sample be a miniature, as it should, on average, mirror a population?

@@

Finite Population Block Kriging (FPBK) is a model-based approach that expands the geostatistical Kriging framework to the finite population setting [@verhoef2008spatial]. Instead of basing inference off of a specific sampling design, we assume the data are generated by a spatial process. @verhoef2008spatial gives details on the theory of FPBK, but some of the basic principles are summarized below. Let $\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}$ be a response vector at locations $s_1$, $s_2$, . . . , $s_N$ that can be measured at the $N$ population units and is represented as an $N \times 1$ vector. Suppose we want to predict some linear function of the response variable, $f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}$, where $\mathbf{b}^\prime$ is a $1 \times N$ vector of weights. For example, if we want to predict the population total across all population units, then we would use a vector of 1's for the weights.

@@

__Jay VH__: Use relative efficiency for figure, using design IRS as the base method.

__Jay VH__: There is not a complete crossing of all simulation factors. We need to add text description about why some independent error settings were excluded.

@@

__Jay VH__: Need to figure out the weird results for n = 50.

__Jay VH__: For the design estimator, verify that the simulation MSPE is equal to the estimated variance for the design estimator, on average, to make sure things are correct for this estimator.

__Jay VH__: Not a ton of difference in grid vs. random so we can consider removing that factor to simplify the presentation, or, put it in an appendix.

### 2021-09-07 inst/SpatialDVM_Manuscript/SpatialDVM_Manuscript.tex
Added Jay's comments to the manuscript.

@@

@@

@@

Finite Population Block Kriging (FPBK) is a model-based approach that
expands the geostatistical Kriging framework to the finite population
setting (Ver Hoef, 2008). Instead of basing inference off of a specific
sampling design, we assume the data are generated by a spatial process.
Ver Hoef (2008) gives details on the theory of FPBK, but some of the
basic principles are summarized below. Let
\(\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}\)
be a response variable that can be measured at the \(N\) population
units and is represented as an \(N \times 1\) vector. Suppose we want to
predict some linear function of the response variable,
\(f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}\), where
\(\mathbf{b}^\prime\) is a \(1 \times N\) vector of weights. For
example, if we want to predict the population total across all
population units, then we would use a vector of 1's for the weights.

@@

@@

>>>>

\textbf{Jay VH}: I think it is important to stress that the limiting
distribution is over all possible randomizations, constrained by
whatever design is used.

\textbf{Jay VH}: quantity is vague. We should stick with variables, or
realized variables (we might also call these values, but we should
define and establish a consistent terminology early on.) \textbf{Matt
H}: I think, though this comment is for this paragraph, we should
establish the terminology earlier.

@@

\textbf{Jay VH}: What about the design for model-based inference?
Strictly speaking, it is fixed -- there is no probabilistic use of a
randomized design. However, we are going to have to deal with Diggle et
al.~(2010).

@@

\textbf{Jay VH}: Saying ``the distribution of the sampled population
units mirrors the density of\ldots{}'' is confusing to me. Are these
formal statistical definitions of distribution (cumulative distribution
function) and density (probability density function)? Wouldn't IRS
sample be a miniature, as it should, on average, mirror a population?

@@

Finite Population Block Kriging (FPBK) is a model-based approach that
expands the geostatistical Kriging framework to the finite population
setting (Ver Hoef, 2008). Instead of basing inference off of a specific
sampling design, we assume the data are generated by a spatial process.
Ver Hoef (2008) gives details on the theory of FPBK, but some of the
basic principles are summarized below. Let
\(\mathbf{z} \equiv \{\text{z}(s_1), \text{z}(s_2), . . . , \text{z}(s_N) \}\)
be a response vector at locations \(s_1\), \(s_2\), . . . , \(s_N\) that
can be measured at the \(N\) population units and is represented as an
\(N \times 1\) vector. Suppose we want to predict some linear function
of the response variable,
\(f(\mathbf{z}) = \mathbf{b}^\prime \mathbf{z}\), where
\(\mathbf{b}^\prime\) is a \(1 \times N\) vector of weights. For
example, if we want to predict the population total across all
population units, then we would use a vector of 1's for the weights.

@@

\textbf{Jay VH}: Use relative efficiency for figure, using design IRS as
the base method.

\textbf{Jay VH}: There is not a complete crossing of all simulation
factors. We need to add text description about why some independent
error settings were excluded.

@@

\textbf{Jay VH}: Need to figure out the weird results for n = 50.

\textbf{Jay VH}: For the design estimator, verify that the simulation
MSPE is equal to the estimated variance for the design estimator, on
average, to make sure things are correct for this estimator.

\textbf{Jay VH}: Not a ton of difference in grid vs.~random so we can
consider removing that factor to simplify the presentation, or, put it
in an appendix.
